Our Title

### 2015-04-30 draft.tex
Updated ignore rules.

@@

\author{\textbf{Contributing Authors:}\\ \\
James	Bevins\\
Christopher	Brand - Naughty...\\
% Christopher	Brand \\
Grant	Buster\\
Denia	Djoki\'{c}\\
Andrew	Greenop\\
Eric	Harvey\\
Tom	Hickey\\
% \'{A}nth\'{o}n\'{y}	J\'{u}\'{a}r\'{e}z\\
Anthony	Juarez\\
Azimbek	Jumakulov - Naughty...\\
% Azimbek	Jumakulov \\
James	Kendrick\\
Nicolas	Mertz - Naughty...\\
Diana	Othman - Naughty...\\
Scott	Parker - Naughty...\\
Bushra	Samimi - Naughty...\\
% Nicolas	Mertz \\
% Diana	Othman \\
% Scott	Parker \\
% Bushra	Samimi \\
Julie	Stabile\\
Andrew	Voyles\\
Xin	Wang
}

@@

Still under development...

@@

Still under development...

\subsection{How does this relate to their potential nuclear interests?}
\subsubsection{????Move in info from mat / signatures group????}

@@

\subsection{??????  Merge with above !?????? }

@@

@@

More than 60 countries have joined the \enquote{global coalition to degrade and defeat ISIL.} The member countries can choose their method and level of participation. Saudi Arabia trains and equips Syrian opposition forces. Jordan’s key role will be intelligence acquiring and sharing. Germany, France, and the United Kingdom are conducting airstrikes.

@@

\subsection{Post-Detonation Forensics Methods}

@@

>>>>

\usepackage{caption}  % Use for \captionof(*) command
\usepackage{pdfpages}

@@

\author{\textbf{Contributing Authors:}\\ \\
James	Bevins\\
% Christopher	Brand - Naughty...\\
Christopher	Brand \\
Grant	Buster\\
Denia	Djoki\'{c}\\
Andrew	Greenop\\
Eric	Harvey\\
Tom	Hickey\\
% \'{A}nth\'{o}n\'{y}	J\'{u}\'{a}r\'{e}z\\
Anthony	Juarez\\
% Azimbek	Jumakulov - Naughty...\\
Azimbek	Jumakulov \\
James	Kendrick\\
% Nicolas	Mertz - Naughty...\\
% Diana	Othman - Naughty...\\
% Scott	Parker - Naughty...\\
% Bushra	Samimi - Naughty...\\
Nicolas	Mertz \\
Diana	Othman \\
Scott	Parker \\
Bushra	Samimi \\
Julie	Stabile\\
Andrew	Voyles\\
Xin	Wang
}

@@

@@

\subsection{How does this relate to their potential nuclear interests?}
\subsubsection{????? Missing ?????}

\subsubsection{????Move in info from mat / signatures group????}

@@

This report was completed as a part of a graduate level Nuclear Security Policy course at the Goldman School of Public Policy and the Nuclear Engineering Department at the University of California, Berkeley. The class of approximately 20, including policy students and nuclear engineering students, was tasked with developing a policy recommendation for preventing ISIL from obtaining any nuclear capabilities.

As this is only a semester long project, there were great restraints on time and therefore scope. This report focuses solely on the paths to ISIL obtaining a nuclear capability. Of course, the fundamental way to preventing this would be to defeat ISIL in its entirety. However, given that the overall destruction of ISIL is a larger administration goal and is therefore being addressed by many other groups, our report focuses solely on nuclear capabilities. We also limited our scope by assuming that this policy applies only to the immediate future, and that if ISIL were to last for a longer time frame, more traditional state non-proliferation activities could take place.

@@

\subsection{???????? Andrew hasn't proofed this section for content yet, just compiled it. From skimming though, it needs some love, as the voice is neither scientific nor professional     ??????????}

\subsection{??????  This makes some nods towards policy, and how to use the fuel cycle in our policy, but not much  ?????????}

\subsection{Uranium}

Regardless of whether nuclear material is destined to be used in a nuclear reactor for power generation or in a nuclear weapon, much of the fuel cycle is the same. Both processes start with the mining of uranium from nature, followed by chemical purification and enrichment \cite{Moody2014}.

The most important step in the process, from a proliferation standpoint, involves enriching the uranium in 235U. Natural uranium is typically 0.72\% \ce{^{235}U} \cite{Benedict1981}.  If uranium is destined for a power plant, it is typically enriched to 3-5\% \ce{^{235}U}. If on the other hand it is going to be used in a weapon, the uranium must be enriched to greater than approximately 90\% \ce{^{235}U} \cite{Moody2014}.

The only true difference in the process of producing uranium for use in a nuclear reactor or in a weapon is the amount of enrichment carried out. Most enrichment is done using gas centrifuges, however this require significant infrastructure that is almost definitely beyond the capabilities of ISIL \cite{Benedict1981}.  Furthermore even if ISIL were able to gain control over an enrichment facility, the length of time it would take them to enrich the uranium for a weapon would likely be long enough to allow other countries to intervene militarily. For example, if ISIL were to gain control of Iran’s Natanz facility, it would take them almost two months to enrich the uranium necessary for a weapon. During that time, there would be obvious tell-tail signs of ISIL attempting to enrich uranium, such as power at that site, without needing to monitor nuclear signatures. Thus the most significant piece of stopping ISIL from enriching uranium for a weapon is simply identifying enrichment facilities, which are difficult to hide, with in its territory.

While ISIL could theoretically use laser separation to enrich uranium, which is significantly more difficult to detect, this is very unlikely. Currently, there is only one prototype process under investigation and it’s in Australia \cite{Moody2014}.  Thus, it seems unlikely that ISIL would be able to use this method to enrich uranium, and thus it does not need to be monitored for.

\subsection{Plutonium}

While uranium appears in nature, plutonium is only available through irradiation in a nuclear reactor \cite{Benedict1981}. It is formed when \ce{^{238}U} undergoes the process known as neutron capture \cite{Benedict1981}.  After a double beta decay, \ce{^{239}Pu}, which can be used in nuclear weapons, is produced. [4] While heavy water reactors do have a higher percentage of \ce{^{238}U}, and thus form \ce{^{239}Pu} at a faster rate, it is possible to also use a light water reactor to produce plutonium \cite{Moody2014}.  While ISIL could theoretically gain control of a commercial nuclear reactor for plutonium production, this seems incredibly unlikely. The only commercial nuclear reactors currently near their territory are located in Iran. [5] Furthermore, while countries like Saudi Arabia, Egypt, Turkey, and the UAE are all moving towards nuclear power, it will be many years before any of those countries have commercial plants. [5] While there are not many commercial reactors that ISIL could easily use to produce plutonium, there are many research reactors scattered throughout the Middle East. [6] However, ISIL would need to make very significant territory gains for any of the closest research reactors to be in danger. [7] Thus, it seems unlikely that ISIL would be able to gain control of a nuclear reactor for plutonium production.

It should be noted that Syria may have had a reactor for the production of plutonium in the past. However, that site was bombed and destroyed by an Israeli airstrike in 2007. [6] It is not impossible that ISIL could obtain the plans for that design. That being said, construction on a nuclear power plant typically takes at least 4 years. [8] Furthermore, nuclear reactors are incredibly difficult to hide, as seen by Israel’s 2007 air raid against Syria. [6] Thus, it seems unlikely that ISIL would be able to complete such a reactor. Therefore, there is a very low probability that ISIL could covertly produce it’s own plutonium, and thus little need to monitor for reprocessing signals from ISIL territory.

\subsection{??????  Add in these refs    ???????}

% [3] “Iran’s Nuclear Timetable,” Wisconisn Projct on Nuclear Arms Control, < http://www.iranwatch.org/our-publications/articles-reports/irans-nuclear-timetable#i>, 24 February, 2015.
% [4] “Nuclear Fission Energy,” Lawrence Berkeley National Laboratory, http://www2.lbl.gov/abc/wallchart/chapters/14/1.html, Accessed: 23 April, 2015.
% [5] “Nuclear Power in the World Today,” World Nuclear Association, <http://www.world-nuclear.org/info/Current-and-Future-Generation/Nuclear-Power-in-the-World-Today/>, February, 2015.
% [6] “Emerging Nuclear Energy Countries,” World Nuclear Association, <http://www.world-nuclear.org/info/Country-Profiles/Others/Emerging-Nuclear-Energy-Countries/>, March 2015.
% [7] “Battle for Iraq and Syria in maps,” BBC, <http://www.bbc.com/news/world-middle-east-27838034>, 24 April, 2015.
% [8] “Building New Nuclear Facilities,” Nuclear Energy Institute, <http://www.nei.org/Issues-Policy/New-Nuclear-Energy-Facilities/Building-New-Nuclear-Facilities>, 2015.

@@

\subsection{??????   Add this reference in   ?????}
[3] JUSTINE DRENNAN, “Who Has Contributed What in the Coalition Against the Islamic State?”, NOVEMBER 12, 2014

More than 60 countries have joined the \enquote{global coalition to degrade and defeat ISIL.} [3] The member countries can choose their method and level of participation. Saudi Arabia trains and equips Syrian opposition forces. Jordan’s key role will be intelligence acquiring and sharing. Germany, France, and the United Kingdom are conducting airstrikes.

@@

\section{Post-Detonation Forensics Methods}

@@

The logic tree can be seen in \autoref{fig:logic_tree}.

\includepdf[angle=270, pagecommand={\thispagestyle{fancy2}\null\vfill\captionof{figure}{Non-linear Logic Tree}\label{fig:logic_tree}}, scale=0.85]{./figures/NucSec_Logic_Model.pdf}
